%\clearemptydoublepage
\newpage

\phantomsection
\addcontentsline{toc}{chapter}{Outline of the Thesis}

\begin{center}
	\huge{Outline of the Thesis}
\end{center}

%--------------------------------------------------------------------
\section*{Part I: Introduction and Theory}

\textbf{ Chapter 1: Introduction}\\
This chapter defines the the scope of the work. The high level
overview of the Monte Carlo methods which are used during the study and
implemented.
The description of the light simulation in the participting media and possible
variance reduction techniques takes place from the general point of view
whithout mathematical formalism. An overview of the advantages and limitations
of the each of the method for practical use is also given in this chapter.

\textbf{Chapter 2: Theory}\\
Chapter 2 contains theorical summary of the Monte Carlo methods with attention
on such concepts, which are important in the context of this work, such
as light integration, importance sampling and multiple importance sampling.
Theory of the in ligth transport in participating media with emission,
attenuation and scattering laws.
The theoretical intoduction into the diffusion theory and diffusion
approximation approach of light integration in participating media.

%--------------------------------------------------------------------
\section*{Part II: Implementation and results}

\textbf{ Chapter 3: Pathtracing integrator and Next Event Estimation}\\
Here the pathtracing implementation details are discussed with additional Direct
Light Sampling technique. Correctness of the method, and
problems in practical usage. Comparison of the performance between two methods
and the combination of them using MIS.

\textbf{ Chapter 4: Diffusion Approximation}\\
The practical details of the implementation of the Diffusion Approximation
light integrator. Sampling starategies and precomputed BSSRDFs. Special case of
the Christenen Burley BSSRDF profile and fitting to Monte-Carlo references.
Importance sampling of the precomputed profiles and and parametrization issues.


\textbf{ Chapter 5: Comparisons and measurements}\\
Rendering of the measured materials. Comparisons between different
implementations. Convergence graphs. \comment{$<$-Currently in TODO status}
